Based on polling as of 27 October 2024, Harris expects to win on 50%, leads Trump by about 3% in 2024 US election

### 2024-10-31 paper/paper.qmd
update data cleaning

In this data-cleaning process, we focus on refining raw polling data to
enhance its quality and relevance for subsequent analysis. The dataset
is initially loaded and cleaned using the janitor package to standardize
column names, ensuring consistency throughout. We then filter the data
to retain only relevant columns and eliminate any rows with missing
values in critical fields, including numeric_grade, pct, sample_size,
and end_date.

Specifically, we isolate the polling data for Kamala Harris and Donald
Trump, applying a condition to include only high-quality polls with a
numeric grade of 2 or higher, given that the mean of the numeric grade
is 2.175 and the median is 1.9.

For state-level polls, we handle any placeholder states marked as "--"
by converting them to NA. A national poll indicator is generated,
assigning a value of 1 for national polls and 0 for state-specific ones.
Dates are standardized using the lubridate package to ensure accurate
handling in subsequent analyses.

Recency weights are calculated based on the number of days elapsed since
the poll ended, utilizing an exponential decay function to give greater
weight to more recent polls.

Finally, the cleaned datasets for both candidates are saved in CSV
format for further modeling and analysis. This systematic approach
guarantees that the data is accurate, complete, and ready for insightful
analysis.

>>>>

In this data-cleaning process, we focus on refining raw polling data for Kamala Harris and Donald Trump to enhance its quality and relevance for analysis. The process begins by loading the dataset and using the janitor package to standardize column names, ensuring consistent naming conventions throughout. We then filter the data to retain only essential columns and remove rows with missing values in key fields, including numeric_grade, pct, sample_size, and end_date.

For each candidate, we isolate polls specifically for Kamala Harris and Donald Trump, retaining only high-quality polls with a numeric_grade of 2 or higher—given that the average numeric_grade is approximately 2.175, with a median of 1.9. We also handle placeholder values in state information by setting entries marked as "--" to NA, and create a national_poll indicator, assigning a value of 1 for national polls and 0 for state-specific ones. Dates are standardized using the lubridate package to facilitate accurate time-based analysis.

Recency weights are calculated based on the days elapsed since the poll's end date, applying an exponential decay function to prioritize more recent polls. Weights based on sample size are capped at a maximum of 2,300 responses to maintain balanced representation. Additionally, categorical variables, including pollster, state, candidate_name, population, and methodology, are converted to factors to prepare for analysis.

The cleaned datasets for both candidates are then saved as Parquet files for efficient storage and access in further modeling and analysis. This structured approach ensures that the data is accurate, complete, and optimized for insightful statistical analysis.
